SNP Analysis

### 2018-07-24 AllSamplesModel.Rmd
regression for snp data

cache.dir = paste(data, 'Analysis/5e6_arms_all_logR', sep='/')

@@

```{r echo=F}
pander(
  as.data.frame(sum.patient.data %>% dplyr::summarise(
  'Total Patients'=length(unique(Patient)),
  'Total Samples'=sum(total.samples),
  'Range'=paste(range(end.year-start.year), collapse='-'),
  'Median Years'=paste(median(end.year-start.year),'+/-',round(sd(end.year-start.year),1)),
  'Median Endoscopies'=paste(median(total.endos),'+/-',round(sd(total.endos),1)),
  'Median age'=paste(median(age.diagnosis),'+/-',round(sd(age.diagnosis),1)),
  'gender F:M'=paste(table(gender),collapse=':')
)), caption='full cohort', justify='left')
```

@@

```{r back, echo=F, message=F, warning=F}
transform.by.time<-function(pt, info) {
  pt = pt[,c('Status','Patient','Hospital.Research.ID','Path.ID','PID','Pathology','Samplename','Final.Endoscopy','Endoscopy.Year','Prediction', 'OR')] %>% group_by(PID, Samplename) %>% dplyr::mutate('months.before.final' = (Final.Endoscopy - Endoscopy.Year)*12)
  pt = dplyr::arrange(merge(pt, subset(info, Hospital.Research.ID == pt$Hospital.Research.ID[1], select=c('Samplename','Block')), by='Samplename'), Pathology, PID, Endoscopy.Year)

>>>>

cache.dir = paste(data, 'Analysis/5e6_arms_all', sep='/')

@@

```{r echo=F}
pander(
  as.data.frame(sum.patient.data %>% dplyr::summarise(
  'Total Patients'=length(unique(Patient)),
  'Total Samples'=sum(total.samples),
  'Range'=paste(range(end.year-start.year), collapse='-'),
  'Median Years'=paste(median(end.year-start.year),'+/-',round(sd(end.year-start.year),1)),
  'Median Endoscopies'=paste(median(total.endos),'+/-',round(sd(total.endos),1)),
  'Median age'=paste(median(age.diagnosis),'+/-',round(sd(age.diagnosis),1)),
  'Median length'=median(M,na.rm=T),
  'gender F:M'=paste(table(gender),collapse=':')
)), caption='full cohort', justify='left')
```

@@

```{r back, echo=F, message=F, warning=F}
transform.by.time<-function(pt, info) {
  pt = pt[,c('Status','Patient','Hospital.Research.ID','Path.ID','PID','Pathology','Maximal','Samplename','Final.Endoscopy','Endoscopy.Year','Prediction', 'OR')] %>% group_by(PID, Samplename) %>% dplyr::mutate('months.before.final' = (Final.Endoscopy - Endoscopy.Year)*12)
  pt = dplyr::arrange(merge(pt, subset(info, Hospital.Research.ID == pt$Hospital.Research.ID[1], select=c('Samplename','Block')), by='Samplename'), Pathology, PID, Endoscopy.Year)

### 2018-07-24 SNP_Prediction_Analysis.Rmd
regression for snp data

@@

```{r, echo=F}

patient.info = patient.info %>% rowwise() %>% dplyr::mutate( Endoscopy = ifelse(Timepoint == 'T1', 1, 2) )

sm = patient.info %>% group_by(Status, Endoscopy, Pathology) %>% dplyr::tally() %>% group_by(Status, Endoscopy) %>% dplyr::mutate(freq=n/sum(n) )
sm$Pathology = factor(sm$Pathology, levels=c('NDBE','ID','LGD','HGD','IMC'), ordered = T)

@@

```{r rnormals, echo=F, warning=F, message=F, fig.width=10, fig.height=8, eval=F}
randNormal = sample(rownames(normalSegs), 1)
pt = unlist(strsplit(randNormal, '_'))[1]
segs = subset(segments.list[[pt]], chr %in% c(1:22) & grepl(sub('_', '.*', randNormal),sample))
segs$chr = factor(segs$chr, levels=c(1:22), ordered = T)

lims = range(segs$medLRR, normalSegs[randNormal,])
# grid.arrange(
#   ggplot(segs) + facet_grid(~chr, space='free_x', scales='free') + ylim(lims) +
#     geom_segment(aes(x=startpos, xend=endpos, y=medLRR, yend=medLRR), size=3) + 
#     theme(axis.text.x=element_blank() ) + labs(title='ASCAT median LRR', subtitle=pt),
#   ggplot(melt(as.matrix(normalSegs[randNormal,])), aes(Var1, value)) + geom_point() + ylim(lims) +
#     labs(title='CN Adjusted & winsorized') + theme(axis.text.x=element_blank()),
# top='Random BLD or gastric normal', bottom=randNormal)

@@

@@

Using the mean bin values (merged during tiling).
```{r, warning=F, message=F, fig.width=10, fig.height=8}
#ns = adjust.cols(normalSegs, z.mean, z.sd)
#ns = adjust.cols(normalSegs)
#range(ns)

@@

#ms = adjust.cols(mergedSegs, z.mean, z.sd)
ms = adjust.cols(mergedSegs)
range(ms)
dim(ms)

@@

#ma = adjust.cols(mergedArms, z.arms.mean, z.arms.sd)
ma = adjust.cols(mergedArms)
range(ma)
dim(ma)

@@

lims=range(arrayDf, allDf,na.rm=T)
grid.arrange(
  ggplot(melt(arrayDf), aes(Var2, value)) + geom_point() + ylim(lims) +
    geom_point(data=melt(arrayDf[,589:634]), col='red') + labs(title='SNP'),
  ggplot(melt(allDf), aes(Var2, value)) + geom_point() + ylim(lims) +
      geom_point(data=melt(allDf[,589:634]), col='red') + labs(title='sWGS'),
nrow=1)

@@

```{r, echo=F, fig.height=12, fig.width=6}
## TODO: quantile normalize the SNP arrays by the sWGS values. 
copy = do.call(cbind.data.frame,lapply(1:ncol(arrayDf), function(i) {
  as.data.frame(normalize.quantiles.use.target(arrayDf[,i,drop=F], as.vector(allDf[,i])))
}))

colnames(copy) = colnames(arrayDf)
rownames(copy) = rownames(arrayDf)

grid.arrange(
  ggplot( melt(allDf), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, sWGS'),
  ggplot( melt(arrayDf), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, SNP arrays'),
  ggplot( melt(copy), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, SNP arrays q-normed'),
  ncol=1
)
arrayDf = as.matrix(copy)
```

```{r, eval=F}
x = apply(mergedSegs, 1, function(x) {
  ds = c()
  for (i in 1:(length(x)-1)) {
    ds = c(ds, abs(x[[i]]) - abs(x[[i+1]]))
  }
  abs(diff(range(ds)))
})
plot(x, col=pred.qc$Status)

x1 = apply(ms, 1, function(x) {
  ds = c()
  for (i in 1:(length(x)-1)) {
    ds = c(ds, abs(x[[i]]) - abs(x[[i+1]]))
  }
  abs(diff(range(ds)))
})
plot(x1, col=pred.qc$Status)

y = apply(normalSegs, 1, function(x) {
  ds = c()
  for (i in 1:(length(x)-1)) {
    ds = c(ds, abs(x[[i]]) - abs(x[[i+1]]))
  }
  abs(diff(range(ds)))
})
plot(y)

range(y)
range(x)

nprgs = subset(pred.qc, Status == 'NP')
prgs = subset(pred.qc, Status == 'P')

t.test(x[prgs$Samplename],x[nprgs$Samplename]) 
t.test(x[prgs$Samplename],y)
t.test(x[nprgs$Samplename],y)
```

@@

# These samples are likely genome duplicated.
dup = subset(pred.qc, `mean(Ploidy)` > 2.7)
cor.test(dup$`mean(Ploidy)`, dup$Prob)
table(dup$Status)

# Three groups, prog, non prog (max LGD), non prog (max HGD)
pred.qc = pred.qc %>% group_by(Status, PatientID) %>% dplyr::mutate( 
  exclude=(Status == 'NP' & (length(which(Pathology == 'HGD')) > 0 | `mean(Ploidy)` > 2.7 )) )
pred.qc$Status = factor(pred.qc$Status)

@@

table(subset(pred.qc, Risk == 'High' & !exclude)$Status)/table(subset(pred.qc, !exclude)$Status)
table(subset(pred.qc, Risk == 'Moderate' & !exclude)$Status)/table(subset(pred.qc, !exclude)$Status)
table(subset(pred.qc, Risk == 'Low' & !exclude)$Status)/table(subset(pred.qc, !exclude)$Status)

# Exclude those odd tetraploidy NPs
#pred.qc[which(with(pred.qc, (Samplename %in% highPloidyCN$Samplename))), 'exclude'] = T
pred.qc[which(pred.qc$PatientID %in% highPloidyCN$PatientID & pred.qc$EndoID %in% highPloidyCN$EndoID), 'exclude'] = T

# Exclude HGD NP patients
roc = pROC::roc(Status ~ Prob, data=subset(pred.qc, !exclude), auc=T, ci=T, of='thresholds')
roc.plot(roc) + labs(title='Excluded low sca/NP tetra), Prob')

per_pt = 
  subset(pred.qc, !exclude) %>% group_by(PatientID, Status) %>% dplyr::summarise( max.Prob = max(Prob), max.RR = max(RR), max.Risk = max(Risk) )
rocpp = pROC::roc(Status ~ max.Prob, data=per_pt, auc=T, ci=T, of='thresholds')
roc.plot(rocpp) + labs(title='Max per patient (excluded low sca/NP tetra), Prob')

# Exclude the low SCA patients
pred.qc[which(pred.qc$PatientID %in% lowsca$PatientID & pred.qc$EndoID %in% lowsca$EndoID), 'exclude'] = T
rocpp = pROC::roc(Status ~ Prob, data=subset(pred.qc, !exclude), auc=T, ci=T, of='thresholds')
roc.plot(rocpp) + labs(title='Max per patient (excluded low sca/NP tetra), Prob')
pROC::coords(rocpp, 'best')

as.data.frame(subset(pred.qc, Status == 'P' & Prob < 0.5 & !exclude))

# Timepoint 2 only
roct2 = pROC::roc(Status ~ Prob, data=subset(pred.qc, Timepoint != 'T1' & !exclude), auc=T, ci=T, of='thresholds')
roc.plot(roct2) + labs(title='T2, Prob')

per_pt_ex = subset(pred.qc, !exclude) %>% group_by(PatientID, Status) %>% dplyr::summarise(
  max.Prob = max(Prob), max.RR = max(RR), max.Risk = max(Risk)
)
rocppex = pROC::roc(Status ~ max.Prob, data=per_pt_ex, auc=T, ci=T, of='thresholds')
roc.plot(rocppex) + labs(title='Max per patient, Prob')

ggplot(subset(pred.qc, !exclude), aes(`mean(SCA.Ratio)`,Prob, color=Risk, shape=Status)) + 
  facet_grid(~Status) + geom_point()

subset(pred.qc, `mean(SCA.Ratio)` < 0.1 & Status == 'P' & !exclude & Prob < 0.5)

ggplot(subset(pred.qc, !exclude | ( `mean(SCA.Ratio)` > 0.1 & Status == 'P')) , aes(`mean(Purity)`,Prob, color=Risk, shape=Status)) + facet_grid(~Status) + geom_point()

ex.pred = subset(pred.qc, !exclude)

# Quick check
nrow(subset(ex.pred, Prob > 0.5 & Status == 'P'))/table(ex.pred$Status)['P']
nrow(subset(ex.pred, Prob < 0.5 & Status == 'P'))/table(ex.pred$Status)['P'] #False negatives

nrow(subset(ex.pred, Prob > 0.5 & Status == 'NP'))/table(ex.pred$Status)['NP'] # False pos
nrow(subset(ex.pred, Prob < 0.5 & Status == 'NP'))/table(ex.pred$Status)['NP'] #

 ggplot(melt(arrayDf), aes(Var2, value)) + geom_point() + 
  geom_point(data=melt(arrayDf['1006_190V',,drop=F]), color='red') + 
  geom_point(data=melt(arrayDf['1044_39Z',,drop=F]), color='blue')

@@

```{r regression, echo=F, message=F}
slabels = as.data.frame(subset(pred.qc, !exclude, select=c('PatientID','Samplename','Status')))
#slabels = as.data.frame(pred.qc, select=c('PatientID','Samplename','Status'))
rownames(slabels) = slabels$Samplename

df = arrayDf[which(rownames(arrayDf) %in% slabels$Samplename),]

status = as.integer(slabels$Status)-1
names(status) = slabels$Samplename

source('lib/cv-pt-glm.R')

nl = 1000;folds = 10; splits = 5 
## ----- All ----- ##
coefs = list(); plots = list(); performance.at.1se = list(); models = list(); cvs = list()
cache.dir = '~/Data/Ellie/Analysis/SNP'
dir.create(cache.dir, recursive = T, showWarnings = F)
file = paste(cache.dir, 'all.pt.alpha.Rdata', sep='/')
if (file.exists(file)) {
 message(paste("loading", file))
 load(file, verbose=T)
} else {
  alpha.values = c(0,0.5,0.7,0.9,1)
  sets = create.patient.sets(slabels, folds, splits, 0.2)

  for (a in alpha.values) {
    message(paste('alpha=',a))
    fit0 <- glmnet(df, status, alpha=a, nlambda=nl, family='binomial', standardize=F)    
    autoplot(fit0) + theme(legend.position="none")
    l = fit0$lambda
    if (a > 0) l = more.l(l)

    cv.patient = crossvalidate.by.patient(x=df, y=status, lambda=l, pts=sets, a=a, nfolds=folds, splits=splits, fit=fit0, select='deviance', opt=-1, standardize=F)

    lambda.opt = cv.patient$lambda.1se

    coef.opt = as.data.frame(non.zero.coef(fit0, lambda.opt))
    coefs[[as.character(a)]] = coef.stability(coef.opt, cv.patient$non.zero.cf)

    plots[[as.character(a)]] = arrangeGrob(cv.patient$plot+ggtitle('Classification'), cv.patient$deviance.plot+ggtitle('Binomial Deviance'), top=paste('alpha=',a,sep=''), ncol=2)

    performance.at.1se[[as.character(a)]] = subset(cv.patient$lambdas, `lambda-1se`)
    models[[as.character(a)]] = fit0
    cvs[[as.character(a)]] = cv.patient
  }
  save(plots, coefs, performance.at.1se, df, models, cvs, labels, file=file)
  p = do.call(grid.arrange, c(plots[ as.character(alpha.values) ], top='All samples, 10fold, 5 splits'))
  ggsave(paste(cache.dir, '/', 'all_samples_cv.png',sep=''), plot = p, scale = 2, width = 12, height = 10, units = "in", dpi = 300)
}
#save(arrayDf,labels,patient.info, file=paste(cache.dir,'snp-models.Rdata',sep='/'))

@@

```{r compare.coefs, echo=F, eval=T}
# Matching
snp.features = coefs$`0.5`

@@

rowSums(snp.features[,-1])/50

@@

```{r loo}

>>>>

patient.info = patient.info %>% rowwise() %>% dplyr::mutate( Endoscopy = ifelse(Timepoint == 'T1', 1, 2) )
```

@@

```{r, echo=F}
sm = patient.info %>% group_by(Status, Endoscopy, Pathology) %>% dplyr::tally() %>% group_by(Status, Endoscopy) %>% dplyr::mutate(freq=n/sum(n) )
sm$Pathology = factor(sm$Pathology, levels=c('NDBE','ID','LGD','HGD','IMC'), ordered = T)

@@

```{r rnormals, echo=F, warning=F, message=F, fig.width=10, fig.height=8, eval=T}
randNormal = sample(rownames(mergedSegs)[nm.rows], 1)
pt = unlist(strsplit(randNormal, '_'))[1]
segs = subset(segments.list[[pt]], chr %in% c(1:22) & grepl(sub('_', '.*', randNormal),sample))
segs$chr = factor(segs$chr, levels=c(1:22), ordered = T)

lims = range(segs$medLRR, mergedSegs[randNormal,])
# grid.arrange(
#   ggplot(segs) + facet_grid(~chr, space='free_x', scales='free') + ylim(lims) +
#     geom_segment(aes(x=startpos, xend=endpos, y=medLRR, yend=medLRR), size=3) + 
#     theme(axis.text.x=element_blank() ) + labs(title='ASCAT median LRR', subtitle=pt),
#   ggplot(melt(as.matrix(normalSegs[randNormal,])), aes(Var1, value)) + geom_point() + ylim(lims) +
#     labs(title='CN Adjusted & winsorized') + theme(axis.text.x=element_blank()),
# top='Random BLD or gastric normal', bottom=randNormal)

@@

Adjust using the RAW values...

```{r raw.adjust, fig.height=16, fig.width=4, echo=T}
q.norm.by<-function(df, target) {
  dfq = do.call(cbind.data.frame,lapply(1:ncol(df), function(i) {
    as.data.frame(normalize.quantiles.use.target(df[,i,drop=F], as.vector(target[,i])))
  }))

  colnames(dfq) = colnames(df)
  rownames(dfq) = rownames(df)

  return(as.matrix(dfq))
}

copySegs = q.norm.by(mergedSegs, raw.segs)
copyArms = q.norm.by(mergedArms, raw.arms)

#copySegs = as.data.frame(normalize.quantiles.use.target(mergedSegs, as.vector(raw.segs)))
grid.arrange(
  ggplot( melt(raw.segs), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, sWGS bins (no arms)'),
  ggplot( melt(mergedSegs), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, SNP bins (no arms)'),
  ggplot( melt(copySegs), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, SNP bins q-normed')
)

@@

Using the mean bin values (merged during tiling).
```{r, warning=F, message=F, fig.width=10, fig.height=8}

#ns = adjust.cols(normalSegs, z.mean, z.sd)
#ns = adjust.cols(normalSegs)
#range(ns)

@@

#ms = adjust.cols(mergedSegs, z.mean, z.sd)
#ms = adjust.cols(mergedSegs)
ms = adjust.cols(copySegs)
range(ms)
dim(ms)

@@

#ma = adjust.cols(mergedArms, z.arms.mean, z.arms.sd)
#ma = adjust.cols(mergedArms)
ma = adjust.cols(copyArms)
range(ma)
dim(ma)

@@

lims=range(arrayDf, dysplasia.df,na.rm=T)
grid.arrange(
  ggplot(melt(arrayDf), aes(Var2, value)) + geom_point() + ylim(lims) +
    geom_point(data=melt(arrayDf[,589:634]), col='red') + labs(title='SNP'),
  ggplot(melt(dysplasia.df), aes(Var2, value)) + geom_point() + ylim(lims) +
      geom_point(data=melt(dysplasia.df[,589:634]), col='red') + labs(title='sWGS'),
nrow=1)

@@

```{r, echo=F, fig.height=12, fig.width=6}
## TODO: quantile normalize the SNP arrays by the sWGS values. 
# copy = do.call(cbind.data.frame,lapply(1:ncol(arrayDf), function(i) {
#   as.data.frame(normalize.quantiles.use.target(arrayDf[,i,drop=F], as.vector(allDf[,i])))
# }))
# 
# colnames(copy) = colnames(arrayDf)
# rownames(copy) = rownames(arrayDf)

grid.arrange(
  ggplot( melt(dysplasia.df), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, sWGS'),
  ggplot( melt(arrayDf), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, SNP arrays'),
  #ggplot( melt(copy), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, SNP arrays q-normed'),
  ncol=1
)
#arrayDf = as.matrix(copy)
```

@@

# Three groups, prog, non prog (max LGD), non prog (max HGD)
# pred.qc = pred.qc %>% group_by(Status, PatientID) %>% dplyr::mutate( 
#   exclude=(Status == 'NP' & (length(which(Pathology == 'HGD')) > 0 | `mean(Ploidy)` > 2.7 )) )
pred.qc$Status = factor(pred.qc$Status)

pred.qc = pred.qc %>% group_by(Status, PatientID) %>% dplyr::mutate(
  exclude=(Status == 'NP' & (length(which(Pathology == 'HGD')) > 0)),
  wgd = (Status == 'NP' & `mean(Ploidy)` > 2.7 )
)
pred.qc = pred.qc %>% group_by(Status, Samplename) %>% dplyr::mutate(
  lowsca = (Status == 'P' & (`mean(SCA.Ratio)` < 0.03 | `mean(Ploidy)` < 1.5))
)

@@

# Exclude HGD NP patients
roc = pROC::roc(Status ~ Prob, data=subset(pred.qc, !exclude), auc=T, ci=T, of='thresholds')
roc.plot(roc) + labs(title='Excluded HGD NP patients')

per_pt = 
  subset(pred.qc, !exclude) %>% group_by(PatientID, Status) %>% dplyr::summarise( max.Prob = max(Prob), max.RR = max(RR), max.Risk = max(Risk) )
rocpp = pROC::roc(Status ~ max.Prob, data=per_pt, auc=T, ci=T, of='thresholds')
roc.plot(rocpp) + labs(title='Max per patient - excluded HGD NP')

# Exclude the low SCA patients
rocpp = pROC::roc(Status ~ Prob, data=subset(pred.qc, !lowsca), auc=T, ci=T, of='thresholds')
roc.plot(rocpp) + labs(title='Both endos - excluded low SCA P')
pROC::coords(rocpp, 'best')

# Exclude the tetraploid NP
rocpp = pROC::roc(Status ~ Prob, data=subset(pred.qc, !wgd), auc=T, ci=T, of='thresholds')
roc.plot(rocpp) + labs(title='Both endos - excluded WGD NP')
pROC::coords(rocpp, 'best')

# Exclude all of the above
rocpp = pROC::roc(Status ~ Prob, data=subset(pred.qc, !exclude & !lowsca & !wgd), auc=T, ci=T, of='thresholds')
roc.plot(rocpp) + labs(title='Both endos - excluded low SCA P & HGD NP & WGD NP')
pROC::coords(rocpp, 'best')

table(subset(pred.qc, Risk == 'High' & !exclude & !lowsca & !wgd)$Status)/table(subset(pred.qc, !exclude & !lowsca & !wgd)$Status)
table(subset(pred.qc, Risk == 'Moderate' & !exclude & !lowsca & !wgd)$Status)/table(subset(pred.qc, !exclude & !lowsca & !wgd)$Status)
table(subset(pred.qc, Risk == 'Low' & !exclude & !lowsca & !wgd)$Status)/table(subset(pred.qc, !exclude & !lowsca & !wgd)$Status)

# Timepoint 2 only
roct2 = pROC::roc(Status ~ Prob, data=subset(pred.qc, Timepoint != 'T1' & !exclude & !lowsca & !wgd), auc=T, ci=T, of='thresholds')
roc.plot(roct2) + labs(title='T2, Prob')

ggplot(subset(pred.qc, !exclude & !wgd & !lowsca), aes(`mean(SCA.Ratio)`,Prob, color=Risk, shape=Status)) + 
  facet_grid(~Status) + geom_point()

ggplot(subset(pred.qc, !exclude & !wgd & !lowsca), aes(`mean(Purity)`,Prob, color=Risk, shape=Status)) + 
  facet_grid(~Status) + geom_point()

ex.pred = subset(pred.qc, !exclude & !wgd & !lowsca)

# Quick check
# nrow(subset(ex.pred, Prob > 0.5 & Status == 'P'))/table(ex.pred$Status)['P']
# nrow(subset(ex.pred, Prob < 0.5 & Status == 'P'))/table(ex.pred$Status)['P'] #False negatives
# 
# nrow(subset(ex.pred, Prob > 0.5 & Status == 'NP'))/table(ex.pred$Status)['NP'] # False pos
# nrow(subset(ex.pred, Prob < 0.5 & Status == 'NP'))/table(ex.pred$Status)['NP'] #
```

@@

```{r regression, echo=F, message=F, eval=T}
## ----- All ----- ##
cache.dir = '~/Data/Ellie/Analysis/SNP'
file = paste(cache.dir, 'all.pt.alpha.Rdata', sep='/')
if (file.exists(file)) {
 message(paste("loading", file))
 load(file, verbose=T)
} else {
  stop("Run 'snp-regression.R' first")
}
#save(arrayDf,labels,patient.info, file=paste(cache.dir,'snp-models.Rdata',sep='/'))

@@

```{r compare.coefs, echo=F, eval=F}
# Matching
snp.features = coefs$`0.5`

@@

length(which(rowSums(snp.features[,-1])/50 > 0.5))

@@

```{r loo, eval=F}
